% !TEX program = lualatex

%% ----------------------------------------------------------------
%% Thesis.tex
%% ----------------------------------------------------------------
\documentclass{ecsthesis}      % Use the Thesis Style
\usepackage[square,numbers]{natbib}  % Use Natbib style for the refs.
\usepackage{graphicx}
\usepackage[version=4]{mhchem}
\usepackage{amsmath}
\usepackage{unicode-math}
\usepackage{braket}
\usepackage{textcomp}
\usepackage{gensymb}
\newcommand{\fig}[1]{Fig.~\ref{#1}}
\newcommand{\eqn}[1]{Eqn.~\ref{#1}}
\hypersetup{colorlinks=true}   % Set to false for black/white printing
\graphicspath{{./}{./Figures/}}   % Location of your graphics files
%% ----------------------------------------------------------------
\begin{document}
\frontmatter
\title      {Applications of Microfluidics in Nuclear Magnetic Resonance}
\authors    {
             {William G Hale}
            }
\addresses  {\groupname\\\deptname\\\univname}
\date       {\today}
\subject    {}
\keywords   {}
\maketitle
\begin{abstract}
  Microfluidics is a constantly growing field of research finding applications in a diverse range of subjects
  such as materials science, chemistry and across the life sciences. This is due to many advantageous attributes
  that microfluidics enjoys, namely small sample volumes which contribute to waste reduction and reduced cost of
  experimentation; highly controllable local environments that enable very precise investigation of changes in
  systems to stimuli; rapid prototyping techniques meaning make, test, tweak cycles can be run more than once
  in a typical day; ease of parallelisation makes gathering statistically significant data much easier without
  the need to repeat experiments for days at a time; and ease of automation increases precision and repeatability

  Nuclear magnetic resonance (NMR) spectroscopy is widely applied technique in chemistry and the life sciences.
  Its non-invasive and non-destructive nature makes it ideal to study living, or mass limited samples. However,
  it is limited by having to have an extremely homogenous magnetic field as well as the low sensitivities possible in a
  typical experiment.

  This thesis describes methods for integrating these two fields. Some NMR experiments being ‘miniaturised’ to
  be performed ‘on-chip’ as well as microfluidic concepts that have been engineered to be compatible with NMR
  techniques. These techniques do not seek to replace established methods of microfluidic analysis such as mass
  spectrometry or fluorescence spectroscopy but could be used to compliment these techniques as an additional
  method of extracting data from the system.

\end{abstract}
\tableofcontents
\listoffigures
\listoftables
\lstlistoflistings
\listofsymbols{ll}{$w$ & The weight vector}
\acknowledgements{I would like to express my deep gratitude to Professor Marcel Utz for his patient guidance and
enthusiastic encouragement that he provided as well as engaging discussion concerning all matters of life and work.
His depth of knowledge in all manner of subjects was a great help throughout my PhD and provided a seemingly endless
source of ideas and problem solving. The principles of scientific investigation I have learnt from him will stay with
me throughout my career.

I wish to thank Professor Malcolm Levitt for his support and guidance, the discussions we have had about science helped
me to see problems in a different light and increased my effectiveness as a scientist.
I am grateful to my colleagues who have helped me enormously throughout my time in Southampton in no particular order I
wish to thank: James Eills, Graeme Finch, Rachel Greenhalgh, Benno Meir, Javier Alonso-Valdesueiro, Karel Kouril, Hana Kourilova,
Aliki Moysiadi, Stuart Elliot, Christian Bengs, Manvendra Sharma, Bishnubatra Partra, Matheus Rossetto, Gabriel Rossetto,
Marek Plata, Sylwia Ostrowska, Weidong Gong, Mohammed Sabba, George Bacanu, Laurynas Dagys, Jo Collel and Barbara Ripka.
To the people that provided support and encouragement throughout my work and helped me keep sane, I am indebted to Frankie
Leeming, Thomas Kear, Laura Jowett, James Eills, Stuart Elliot, Christian Bengs, Aliki Moysiadi, Nic Charles, Judy Fox, Josie
Charles, Gemma Charles and Eddie Robinson you all helped immensely.

In particular I’d like to thank Alyssa Charles for her unwavering support, encouragement and belief in me, as well as proof
reading and correcting my grammar errors.

Finally, I’d like to thank my family for all their support over the years, this is all possible because of them.}
\dedicatory{To my family}
\mainmatter
%% ----------------------------------------------------------------
\include{Introduction}
\include{chapter-droplets}
\include{chapter-ph2}
\include{chapter-peristaltics}
\include{Conclusions}
%\appendix
%\include{AppendixA}
\bibliographystyle{rsc}
\bibliography{literature}
\end{document}
%% ----------------------------------------------------------------
